---
title: "Module2Quiz2"
author: "John Scull"
date: "5/30/2022"
output: word_document
---

Libraries
```{r}
library(tidyverse)
library(tidymodels)
library(glmnet) 
library(GGally)
library(ggcorrplot) 
library(MASS)
library(car) 
library(lubridate)
library(lmtest)
library(splines)
```

```{r}
library(readr)
bike_cleaned <- read_csv("~/Documents/BAN 502/Module 2/bike_cleaned.csv")
```

```{r}
bike = bike_cleaned
bike = bike %>% mutate(dteday = mdy(dteday))
bike = bike %>% mutate_if(is.character, as_factor)
bike = bike %>% mutate(hr = as_factor(hr))
summary(bike)
```


Question 1 Which of the quantitative variables appears to be best correlated with “count”? NOTE: Ignore
the “registered” and “casual” variable as the sum of these two variables equals “count”. Because these
variables combine to make the response variable, they cannot be used as predictors. You can also ignore the
“instant” variable as it is just a row number.
A. windspeed
B. hum
C. atemp
D. *temp*
```{r}
ggcorr(bike,label = TRUE,label_round = 2)
```


Repeat this boxplot-based analysis for each of the categorical variables.
```{r}
ggplot(bike,aes(x=temp,y=count)) + geom_boxplot() + theme_bw()
ggplot(bike,aes(x=hr,y=count)) + geom_boxplot() + theme_bw()
ggplot(bike,aes(x=atemp,y=count)) + geom_boxplot() + theme_bw()
ggplot(bike,aes(x=instant,y=count)) + geom_boxplot() + theme_bw()
ggplot(bike,aes(x=hum,y=count)) + geom_boxplot() + theme_bw()
ggplot(bike,aes(x=windspeed,y=count)) + geom_boxplot() + theme_bw()
ggplot(bike,aes(x=casual,y=count)) + geom_boxplot() + theme_bw()
ggplot(bike,aes(x=registered,y=count)) + geom_boxplot() + theme_bw()
ggplot(bike,aes(x=season,y=count)) + geom_boxplot() + theme_bw()
ggplot(bike,aes(x=dteday,y=count)) + geom_boxplot() + theme_bw()
ggplot(bike,aes(x=mnth,y=count)) + geom_boxplot() + theme_bw()
ggplot(bike,aes(x=hr,y=count)) + geom_boxplot() + theme_bw()
ggplot(bike,aes(x=holiday,y=count)) + geom_boxplot() + theme_bw()
ggplot(bike,aes(x=weekday,y=count)) + geom_boxplot() + theme_bw()
ggplot(bike,aes(x=workingday,y=count)) + geom_boxplot() + theme_bw()
ggplot(bike,aes(x=weathersit,y=count)) + geom_boxplot() + theme_bw()
```
Question 2 Which “season” appears to have the highest count of rides?
A. Winter
B. Spring
C. *Summer*
D. Fall

Question 3 Build a linear regression model (using tidymodels) with “hr” to predict “count”. You will use
this model to answer the next several questions.
```{r}
bike_recipe = recipe(count ~ hr, bike) %>%
  step_dummy(all_nominal())

lm_model = #give the model type a name 
  linear_reg() %>% #specify that we are doing linear regression
  set_engine("lm") #specify the specify type of linear tool we want to use 

lm_wflow = 
  workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(bike_recipe)

lm_fit = fit(lm_wflow, bike)
```

```{r}
summary(lm_fit$fit$fit$fit)
```

How many dummy (indicator) variables are used to represent “hr” in the model? *23*

Question 4 In your model from Question 3, which hour is selected as the “base” level (category)? The base
level does not have an associated coefficient (slope) in the linear regression model. *0*

Question 5 During which hour of the day does the model predict the highest number of rides? *17*

Question 6 Plot “temp” (x axis) versus “count” (y axis) using an appropriate plot type.
```{r}
ggplot(bike,aes(x=temp,y=count)) + geom_point() + theme_bw()
```

Which statement best describes the general relationship between “temp” and “count”?
A. *As “temp” increases, “count” appears to generally increase.*
B. As “temp” increases, “count” appears to generally decrease.
C. There does not appear to be a relationship between “temp” and “count”.

Question 7 Create a linear regression model (using tidymodels) with “hr” and “temp” to predict “count”.
You will use this model to answer the next several questions.

```{r}
bike_recipe = recipe(count ~ hr + temp, bike) %>%
  step_dummy(all_nominal())

lm_model = #give the model type a name 
  linear_reg() %>% #specify that we are doing linear regression
  set_engine("lm") #specify the specify type of linear tool we want to use 

lm_wflow = 
  workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(bike_recipe)

lm_fit2 = fit(lm_wflow, bike)
```

```{r}
summary(lm_fit2$fit$fit$fit)
```

What is the value of the slope coefficient for “hr23” in this model (to three decimal places)? *31.748*

Question 8 What is the adjusted R-squared value (to four decimal places) for the model from Question 7? *0.5886*

Question 9 Create a linear regression model (using tidymodels as usual) with “temp” and “atemp” to predict
“count”. 
```{r}
bike_recipe = recipe(count ~ temp + atemp, bike) %>%
  step_dummy(all_nominal())

lm_model = #give the model type a name 
  linear_reg() %>% #specify that we are doing linear regression
  set_engine("lm") #specify the specify type of linear tool we want to use 

lm_wflow = 
  workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(bike_recipe)

lm_fit3 = fit(lm_wflow, bike)
```

```{r}
summary(lm_fit3$fit$fit$fit)
```


What is the adjusted R-squared value (to four decimal places) of this model? *0.1638*

Question 10 Which of the two variables in the model from Question 9 are significant?
A. *temp ONLY*
B. atemp ONLY
C. Neither temp nor atemp are significant
D. Both temp and atemp are significant

Question 11 The model from Question 9 likely demonstrates which phenomenon?
A. Non-constant variance of residuals
B. Non-normality of residuals
C. *Multicollinearity*
D. None of these

Question 12 Build a backward stepwise regression model to predict “count”. Your “allmod” (the starting
model) should include the following variables: season, mnth, hr, holiday, weekday, workingday, weathersit,
temp, atemp, hum, and windspeed.
```{R}
allmod = lm(count ~ season + mnth + hr + holiday + weekday + workingday + weathersit + temp + atemp + hum + windspeed, bike) #use the ~. to include all predictors rather than typing them all in
summary(allmod)

emptymod = lm(count ~1, bike) #use ~1 to build an empty model 
summary(emptymod)
```

```{r}
#backward
backmod = stepAIC(allmod, direction = "backward", trace = TRUE) #trace = TRUE shows how the model is built (which variables are removed)
summary(backmod)
```

In the “allmod” you should see that the “workingday” variable appears with “NA” values in the model
summary. This is happening because “workingday” is a perfect combination of two other predictor variables.
Which two variables combine to make “workingday”?
A. season and mnth
B. *weekday and holiday*
C. hr and mnth
D. season and mnth

Question 13 The backward stepwise method removes only one variable. Which variable is removed?
A. windspeed
B. *workingday*
C. hum
D. holiday