##Quiz 1
###Module 2

```{r}
library(tidyverse)
library(tidymodels)
library(GGally)
library(lmtest)
library(ggcorrplot)
```

Read-in Data
```{r}
air = airquality
```

Question 1 How many rows are in the “air” dataframe? *153*
```{r}
nrow(airquality)
```

Question 2 How many columns are in the “air” dataframe? *6*
```{r}
ncol(airquality)
```



Question 3 True/False: There is missing data in “Ozone” variable in the dataframe. *True*
```{r}
str(air)
summary(air)
```

```{r}
ggpairs(air)
```


Question 4 Which variable is most likely to be the response (Y) variable? *Ozone*
A. Ozone
B. Solar.R
C. Wind
D. Temp
E. Month
F. Day

```{r}
air2 = air %>% drop_na()
```


Question 5 How many rows remain in this new (air2) data frame? *111*
```{r}
nrow(air2)
```



Question 6 How many columns remain in this new (air2) data frame? *6*
```{r}
ncol(air2)
```


Question 7 Which variable is most strongly correlated with the “Ozone” variable?
A. Solar.R
B. Wind
C. *Temp*
D. Month
E. Day
```{r}
ggpairs(air2)
```
```{r}
p1 = ggplot(air2, aes(x=Solar.R,y=Ozone)) + geom_point(alpha=0.1) #changing alpha is helpful when many points may overlap
p2 = ggplot(air2, aes(x=Wind,y=Ozone)) + geom_point(alpha=0.1)
p3 = ggplot(air2, aes(x=Temp,y=Ozone)) + geom_point(alpha=0.1)
p4 = ggplot(air2, aes(x=Month,y=Ozone)) + geom_point(alpha=0.1)
p5 = ggplot(air2, aes(x=Day,y=Ozone)) + geom_point(alpha=0.1)
grid.arrange(p1,p2,p3,p4,p5,ncol=2)
```

```{r}
ggcorr(air2, method = c("pairwise", "pearson"),cor_matrix = NULL,nbreaks = NULL,digits = 2,name = "ozone",low = "#3B9AB2",mid = "#EEEEEE",high = "#F21A00",midpoint = 0,palette = NULL,geom = "tile",min_size = 2,max_size = 6,label = TRUE,label_alpha = FALSE,label_color = "black",label_round = 1,label_size = 4,limits = c(-1, 1),drop = is.null(limits) || identical(limits, FALSE),layout.exp = 0,legend.position = "right",legend.size = 9)
```


Question 8 Which variable is least strongly correlated with the “Ozone” variable?
A. Solar.R
B. Wind
C. Temp
D. Month
E. *Day*


Question 9 Plot “Temp” (x axis) versus “Ozone” (y axis) using the “ggplot” function. Choose an appropriate
chart type. Which statement best describes the relationship between “Temp” and “Ozone”?
A. As Temp increases, Ozone decreases
B. As Temp increases there is no noticeable change in Ozone
C. *As Temp increases, Ozone increases*
```{r}
ggplot(air2,aes(x=Temp,y=Ozone)) + geom_point(alpha=0.5) + theme_bw()
```


Question 10 What is the slope of this regression model (to four decimal places)? *2.4391*
```{r Non Tidy approach}
mod2 = lm(Ozone ~ Temp, air2) #create linear regression model
summary(mod2) #examine the model
```

```{r}
ggplot(air2,aes(x=Temp,y=Ozone)) + geom_point(alpha=0.1) + geom_smooth(method = "lm", color = "red") + theme_bw()
```

```{r}
air2_simple = recipe(Ozone ~ Temp, air2)
air2_simple
```

```{r}
lm_air2 = #give the model type a name 
  linear_reg() %>% #specify that we are doing linear regression
  set_engine("lm") #specify the specify type of linear tool we want to use 
```

```{r}
lm_wflow = 
  workflow() %>% 
  add_model(lm_air2) %>% 
  add_recipe(air2_simple)
```

Next we fit (execute) the workflow on our dataset.  
```{r}
lm_fit = fit(lm_wflow, air2)
```

```{r}
summary(lm_fit$fit$fit$fit) #three fits :), the actual fit is embedded deeply in the object
```



Question 11 what is the R-squared value of this model (not Adjusted R-squared) (to three decimal places)?
*0.488*

Question 12 Is the “Temp” variables significant in the model?
*Yes*

Question 13 Use the code below to generate 95% confidence intervals for the coefficients. Note that you
may need to change “lm_fit” to the name of your model fit if you used a different name.
True/False: A 95% confidence interval for the slope coefficient does not contain zero.

```{r}
confint(lm_fit$fit$fit$fit)
```


Question 14: Using your linear regression model with “Temp” to predict “Ozone”, what is the predicted
“Ozone” value when “Temp” is equal to 80 (to two decimal places)? *47.48*

```{r}
#Manually
-147.6461 + 2.4391*80
```


Question 15 Perform appropriate model diagnostics to verify whether or not the model appears to meet the
four linear regression model assumptions.
True/False: There is no evidence of non-independent (autocorrelated) residuals. *True*
*Assumption1 - yes - linear*

*Assumption 2 - DW Test*
```{r}
dwtest(lm_fit$fit$fit$fit)
```

*Assumption 3*
```{r}
air3 = air2 %>% mutate(resid1 = lm_fit$fit$fit$fit$residuals) #add the model residuals to our data frame
ggplot(air3,aes(x=Temp,y=resid1)) + geom_point() + theme_bw()
```
*Assumption 4 - Normally Distributed*
```{r}
ggplot(air3,aes(x=resid1)) + geom_histogram() + theme_bw()
```

